Model Support

### 2022-12-21 README.Rmd
changed package name to clarify and simmi to misim

# `simbased`: Simulation-Based Inference for Regression Models

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/simbased)](https://CRAN.R-project.org/package=simbased)
<!-- badges: end -->

`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.

@@

You can install the development version of `simbased` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ngreifer/simbased")
```
## Introduction

@@

The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

```{r example, fig.width=7, fig.height=3}
library(simbased)

@@

`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

@@

We can also use `simbased` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

@@

`simbased` offers parallel processing for all estimation functions to speed up computation.

>>>>

# `{clarify}`: Simulation-Based Inference for Regression Models

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/clarify)](https://CRAN.R-project.org/package=clarify)
<!-- badges: end -->

`{clarify}` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.

@@

You can install the development version of `{clarify}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ngreifer/clarify")
```
## Introduction

@@

The `{clarify}` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `{clarify}` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

```{r example, fig.width=7, fig.height=3}
library(clarify)

@@

`{clarify}` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

@@

We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

@@

`{clarify}` offers parallel processing for all estimation functions to speed up computation.

### 2022-12-21 _dev/supported_models.Rmd
changed package name to clarify and simmi to misim

@@

Need to add tests and examples

@@

@@

@@

* Add `transform_coefs()` (probably okay unless `coef()` doesn't return a vector)
* Add `get_vcov()` (probably okay)
* Add `get_df()` (probably set to `Inf` unless model is a linear model fit with OLS)
* Add `get_coef_template()` (probably okay unless coefficients stored in unusual way)
* Add `untransform_coefs()` (probably okay unless coefficients stored in unusual way)
* Add `get_coef_location()` (probably `"coefficients"`)
* Add `simbased_predict()` (probably okay unless multivariate)
* Add test to `test-sim.R` and `test-sim_ame.R`

>>>>

* `robustbase::lmrob()`, `robustbase::glmrob()`

* `robust::lmRob()`, `robust::glmRob()`

* `AER::tobit()`

@@

Need to add examples

@@

* Quantile regression (`quantreg::rq()`)

@@

* SEM (`lavaan`)

@@

* Add `transform_coefs()` (probably okay unless `coef()` doesn't return a vector)
* Add `get_vcov()` (probably okay)
* Add `get_df()` (probably set to `Inf` unless model is a linear model fit with OLS)
* Add `get_coef_location()` (probably `"coefficients"`)
* Add `get_coef_template()` (probably okay unless coefficients stored in unusual way)
* Add `untransform_coefs()` (probably okay unless coefficients stored in unusual way)
* Add `simbased_predict()`
* Add test to `test-sim.R` and `test-sim_ame.R`
